\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\title{README / User Manual\\\large Autonomous Driving Without Lane Marks}
\author{Humayra Rashid, Daniel gomez, Henry Xiong, Rodrigo Valdez}
\date{\today}

\begin{document}
\maketitle


\section*{Jira Link}
\textbf{Project Board:} \url{https://cs3338-03-group-5.atlassian.net/jira/software/projects/ADC/boards/6}

\section{Project Overview}
This project provides a modular algorithm for autonomous vehicles to navigate safely on roads without clear or reliable lane markings. It includes a software simulation and hardware prototype tested on a toy vehicle.

\section{Formal Objectives}
\begin{itemize}
  \item Develop an autonomous driving algorithm that operates in the absence of visible lane markers.
  \item Test and validate the algorithm using both simulated and physical environments.
  \item Ensure modularity and portability of the algorithm to different hardware platforms.
\end{itemize}

\section{Project Goals and Rationale}
\textbf{Why is this needed?} Traditional autonomous driving models rely heavily on lane detection, which can fail in poor weather, construction zones, or unmarked roads. This system enhances safety and adaptability in such scenarios.

\textbf{Key Goals:}
\begin{itemize}
  \item Increase robustness of autonomous vehicle navigation
  \item Build an affordable, scalable test platform for algorithm development
  \item Contribute to the open-source autonomous driving community
\end{itemize}

\section{How to Access and Run the System}
\subsection*{1. Clone the Repository}
\begin{verbatim}
$ git clone https://github.com/TeamCoolKats/Autonomous-Driving-Car
\end{verbatim}

\subsection*{2. Install Dependencies}
\begin{itemize}
  \item Python 3.9 or higher
  \item OpenCV
  \item NumPy
  \item For C++ modules: g++ or VS Code with C++ extension
\end{itemize}

\subsection*{3. Run in Simulator}
Instructions are in the `simulator/README.md`. Use a simulator like CARLA or a custom test harness.

\subsection*{4. Run on Prototype Vehicle}
See `prototype/setup.md`. Use Raspberry Pi with camera module and motor driver controller.

\section{Folder Structure}
\begin{verbatim}
/algorithm      - Contains processing and response modules
/simulator      - Contains simulation scripts and scenarios
/prototype      - Setup guides and wiring diagrams for hardware
/docs           - Design documents, SRS, and snapshots
/tests          - Unit and integration tests
\end{verbatim}

\section{Support and Contributions}
\begin{itemize}
  \item Contact the repo owner via GitHub issues for bugs or suggestions.
  \item Contributions are welcome through pull requests after discussion.
\end{itemize}

\section{License}
This project is licensed under the MIT License. For educational use only.

\end{document}
